---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

devtools::load_all()
```

# pathr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/pathr)](https://CRAN.R-project.org/package=pathr)
[![Codecov test coverage](https://codecov.io/gh/KoderKow/pathr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/KoderKow/pathr?branch=main)
[![R-CMD-check](https://github.com/KoderKow/pathr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/KoderKow/pathr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of pathr is to simplify the process of string manipulations for URLs and file paths. This uses modified functions from the [{httr}](https://github.com/r-lib/httr) to create opinionated functions that allow working with URLs and paths easier.

## Installation

You can install the development version of pathr like so:

``` r
devtools::install_github("koderkow/pathr")
```

## URLs

### Basic URLs

```r
library(pathr)
```

Sort components of a URL

```{r parse}
url <- "https://github.com/KoderKow/pathr"

x <- parse_url(url)

x

str(x)
```

Put it back to together

```{r}
build_url(x)
```

### URLs with a file path

URLs with item paths will be detected

```{r}
url <- "https://github.com/KoderKow/pathr/example-folder/my-data.csv"

x <- parse_url(url)

x

str(x)
```

Building the URL ignores the file element

```{r}
build_url(x)
```

## Thanks to

- [{httr}](https://github.com/r-lib/httr) package for the code for `parse_url()` and `build_url()`
